---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OmopBridge

<!-- badges: start -->
[![R-CMD-check](https://github.com/oxford-pharmacoepi/OmopBridge/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/oxford-pharmacoepi/OmopBridge/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/oxford-pharmacoepi/OmopBridge/graph/badge.svg)](https://app.codecov.io/gh/oxford-pharmacoepi/OmopBridge)
<!-- badges: end -->

OmopBridge lets you save named database configurations in a user-level
`.Renviron` file and create an OMOP CDM connection from a key.

## Installation

You can install the development version of OmopBridge from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("oxford-pharmacoepi/OmopBridge")
```

## Example

Set up a PostgreSQL configuration once. The password is prompted for when it
is omitted and is not printed by the package.

```{r setup, eval = FALSE}
library(OmopBridge)

setupDatabaseKey(
  key = "postgres_omop",
  dbms = "postgres",
  server = "localhost",
  database = "omop",
  uid = "my-user",
  cdmSchema = "cdm",
  resultsSchema = "results",
  achillesSchema = "achilles"
)
```

Create the CDM reference whenever it is needed:

```{r connect, eval = FALSE}
cdm <- cdmFromKey("postgres_omop")
```

Configurations can be inspected without exposing the password:

```{r inspect, eval = FALSE}
databaseConfig("postgres_omop")
```

For SQL Server, provide an explicit catalog for each schema:

```{r sql-server, eval = FALSE}
setupDatabaseKey(
  key = "sql_server_omop",
  dbms = "sql server",
  server = "sql-server",
  database = "connection_database",
  uid = "my-user",
  cdmCatalog = "omop",
  cdmSchema = "dbo",
  resultsCatalog = "results",
  resultsSchema = "dbo",
  achillesCatalog = "results",
  achillesSchema = "achilles"
)
```

The `.Renviron` file contains credentials and should never be committed to
version control.
